### 2009-11-18 src/Docs/Intro.tex
Intro: add a Recommended Reading section

We really should right something informative here.

>>>>

We really should write something informative here.

\subsection{Recommended readings}

The type-checker is a bidirectional
one~\cite{turner:bidirectional_tc}. A remotely related type-checker
has been described in the context of ETT~\cite{chapman:ett}.

Normalization is achieved by evaluation~\cite{dybjer:nbe,
  dybjer:dependent_types_work}. The implementation has been described
in James Chapman's work~\cite{chapman:phd}. A graspable introduction
to both normalization by evaluation and bidirectional type-checking
\`a la Epigram can be found in Boutillier's
report~\cite{boutillier:report}.

The story for names has been told by McBride and
McKinna~\cite{mcbride:free_variable}. \emph{Ite messa est}.

For containers, there is a lot to say. So, I will not say anything for
the moment.
